Data Structures Comparative Review Thing

### 2014-04-15 paper/paper.tex
rewrote the implementation section

    \section{Implementation}

    We used C++ as the implementation language.  libstdc++'s implementations of the standard
    class templates \texttt{std::map} and \texttt{std::unordered\_map} were used for the binary search
    tree and the hash table respectively.  As the C++ standard library lacks a skip list\footnote{reference to
    the standard here}, we used an open-source third party library, \texttt{CSSkipList}\footnote{reference to
    library home page here}.

    For our measurements, we used libstdc++'s implementation of the standard
    \texttt{std::chrono::high\_resolution\_clock} class was used for time measurements.   Memory
    measurements were performed by providing a custom allocator which tracked the number of memory
    requests.  Note that the latter is a step away from our initial plan, where we stated we would use
    the POSIX API\footnote{ref to the posix api}; unfortunately, that turned out to be too coarse-grained
    for our purposes and we could thus get no accurate measurements that way.  The allocator-based technique
    we employed required slight modifications to the skip list implementation we used, but this
    shouldn't have caused a significant slowdown (if anything, it made things more fair, as now allocation
    was done the same way in both systems).

>>>>

    \section{Implementation}
    \subsubsection*{Datastructures}

    Using C++ as the implementation language, we chose libstdc++'s implementations of the standard class
    templates \texttt{std::map} and \texttt{std::unordered\_map} for the binary search
    tree and the hash table respectively.  As the C++ standard library does not contain a skip
    list\footnote{reference to the standard here}, we used an open-source third party library,
    \texttt{CSSkipList}\footnote{reference to library home page here}.  We also used libstdc++'s
    implementation of \texttt{std::string} for our string handling\footnote{specify?}needs.

    \subsubsection*{Data}
    For our data, we took the system's dictionary file and the list of top level domains from Wikipedia
    and combined these to generate a list of items in the form \texttt{www.\$word.\$tld}, where
    \texttt{\$word} is one of words from the the dictionary and \texttt{\$tld} is a top level domain.  Only
    words consisting of the lowercase letters \texttt{a} through \texttt{z} were used.  Constraining the
    words to consist of 8 to 12 characters and limiting the top-level domains to exactly two letters, 
    all possible combinations were generated.  For the full paths, a number of domains was selected
    and each was appended a random alphanumeric string of eighty characters.  The exact implementation
    can be viewed in the sourcecode\footnote{ref to apendix or code dump}.

	\subsubsection*{Measurements}
    For our time measurements, we used libstdc++'s implementation of the standard
    \texttt{std::chrono::high\_resolution\_clock} class.

    Memory measurements were performed by providing a custom allocator which tracked the number of memory
    requests.  Note that the latter deviates from our initial plan, where we stated\footnote{ref?}we would
    use the POSIX API\footnote{ref to the posix api}.  Unfortunately, that turned out to be too
    coarse-grained for our purposes and we could thus get no accurate measurements.  The
    allocator-based technique we employed did require some slight modifications to the skip list
    implementation we used, but this should not have caused a significant slowdown. We assume that any 
    influence will only have made the tests more fair, as now allocation was done the same way in all 
    three setups.

    After some tests we chose to decrease the number of runs used for measurements.  In the
    proposal we stated that for each time measurement we would perform the relevant operation 1000
    times and then take the average of that.  In practice, this made the tests run for longer than
    we could afford. Because the results given by performing 100 runs were comparable, we settled for that.  
    We expect the general result to be similar; refer to section\footnote{ref}for details
    about what \emph{could} have gone wrong.
